### 2008-09-04 doc/client/client_technical.tex
more text

All capabilities are enabled for three different grid flavours (Production ARC, ARC1 and gLite) 
through the modular design using plugins specialized for each supported middleware. Future 
extensions to support additional middlewares involve plugin compilation only i.e. no recompilation 
of main libraries or client.

@@

\begin{figure}[ht]
\centering{{\scalebox{0.75}{\includegraphics{TargetDiscovery.png}}}
\caption{\label{fig:ResDisc}Diagram depicting the process of resource discovery and information retrieval.} }
\end{figure}

@@

\begin{figure}[ht]
\centering{{\scalebox{0.75}{\includegraphics{JobSubmission.png}}}
\caption{\label{fig:JobSub}Diagram depicting the process of submitting a job to a computing service.}}
\end{figure}

@@

\section{Job Management}
Information about active jobs is stored in a local xml file which is used for later job management. As this file may contain 
information about jobs running on completely different grid flavours, job management should be handled using plugins similar to 
resource discovery and job submission. The following classes are used:

@@

\begin{enumerate}
\item{Try reading system configuration from \texttt{<ARC Install Location>/etc/arcclient.xml}}
\item{If the previous step failed try reading system configuration from \texttt{/etc/arcclient.xml}}
\item{Merge system and user configuration by adding all system configuration not already listed 
in the user configuration to the latter.}
\item{Check if \texttt{\$X509\_USER\_PROXY} is set, if set add this as \texttt{ProxyPath} to configuration}
\end{enumerate}

>>>>

All capabilities are enabled for three different grid flavours (Production ARC, ARC1 and gLite) 
through a modular design using plugins specialized for each supported middleware. Future 
extensions to support additional middlewares involve plugin compilation only i.e. no recompilation 
of main libraries or client.

@@

\begin{figure}[ht]
\centering{{\scalebox{0.75}{\includegraphics{TargetDiscovery.png}}}
\caption{\label{fig:ResDisc}Diagram depicting the resource discovery and information retrieval process} }
\end{figure}

@@

\begin{figure}[ht]
\centering{{\scalebox{0.75}{\includegraphics{JobSubmission.png}}}
\caption{\label{fig:JobSub}Diagram depicting the submission of a job to a computing service.}}
\end{figure}

@@

\section{Job Management}
Once a job is submitted job related information (job identification string, cluster etc) is stored in a local xml file which hosts 
similar information for all active jobs. This file may contain jobs runnng on completely different grid flavour, and thus job 
management should be handled using plugins similar to resource discovery and job submission. The job managing plugin is called 
the {\JobController} and it is supported by the {\JobSupervisor} and {\Job} classes.

\begin{figure}[ht]
\centering{{\scalebox{0.75}{\includegraphics{JobManagement.png}}}
\caption{\label{fig:JobMan}Diagram depicting how job controlling plugins, {\JobController}s, are loaded and initialized.}}
\end{figure}

Figure~\ref{fig:JobMan} shows how the three different classes work together and below a step by step description is given:

\begin{enumerate}
\item{The {\JobSupervisor} takes three arguments Jobs (job identification strings), ClusterSelect and ClusterReject.}
\item{A job identification string does not uniguely define which grid flavour runs a certain job. Thus this information is stored 
in joblist.xml upon submission by the {\Submitter} and joblist.xml is extensively used by the {\JobSupervisor} to identify the 
{\JobController} flavours which are to be loaded.}
\item{Suitable {\JobController}s are loaded}
\item{Jobs, ClusterSelect and ClusterReject are passed to the {\JobController} which uses the information to 
fill its internal JobStore.}
\item{Residing within the {\JobSupervisor} the {\JobController}s are now accesible for external calls (i.e. job handling).}
\end{enumerate}

@@

\begin{enumerate}
\item{Try reading system configuration from \texttt{<ARC Install Location>/etc/arcclient.xml}}
\item{If the previous step failed try reading system configuration from \texttt{/etc/arcclient.xml}}
\item{Merge system and user configuration by adding all system configuration not already listed 
in the user configuration to the latter.}
\item{Check if \texttt{\$X509\_USER\_PROXY} is set, if set add this as \texttt{ProxyPath} to configuration}
\item{If \texttt{\$X509\_USER\_PROXY} is not set and configuration tree does not already contain 
a \texttt{ProxyPath} set \texttt{ProxyPath} to \texttt{/tmp/x509up\_u + userid}.}
\item{Check if \texttt{\$X509\_USER\_CERT} is set, if set add this as \texttt{CertificatePath} to configuration}
\item{If \texttt{\$X509\_USER\_CERT} is not set and configuration tree does not already contain 
a \texttt{CertificatePath} set \texttt{CertificatePath} to \texttt{/etc/grid-security/hostcert.pem} 
if user is superuser otherwise \texttt{\$HOME/.globus/usercert.pem}.}
\item{Check if \texttt{\$X509\_USER\_KEY} is set, if set add this as \texttt{KeyPath} to configuration}
\item{If \texttt{\$X509\_USER\_KEY} is not set and configuration tree does not already contain 
a \texttt{KeyPath} set \texttt{KeyPath} to \texttt{/etc/grid-security/hostkey.pem} 
if user is superuser otherwise \texttt{\$HOME/.globus/userkey.pem}.}
\item{Check if \texttt{\$X509\_CERT\_DIR} is set, if set add this as \texttt{CACertificatesDir} to configuration}
\item{If \texttt{\$X509\_CERT\_DIR} is not set and configuration tree does not already contain 
a \texttt{CACertificatesDir} set \texttt{CACertificatesDir} to \texttt{/etc/grid-security/certificates}.}
\end{enumerate}
